---
title: "SDL PAND - Mapa global"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: scroll
    favicon: favicon.ico
---

## SDL-PAND KPIs Model actual

```{r echo=FALSE, message=FALSE, warning=FALSE}
library(flexdashboard)
library("knitr")
library("RSocrata")
library(plotly)
library(personograph)
library(dplyr)
library(rococo)
library(EpiEstim)
library(lmtest)

knitr::opts_chunk$set(echo = TRUE)

read_chunk('common.R')
```

```{r functions, echo=FALSE, message=FALSE, warning=FALSE}

```

```{r setup, echo=FALSE}
# DIGITAL SHADOW
# ##################################################################################

PoblacioTotal = 7566000
regio = ""

casos <- read.socrata("https://analisi.transparenciacatalunya.cat/api/odata/v4/623z-r97q")
casosTotal <- read.socrata("https://analisi.transparenciacatalunya.cat/api/odata/v4/qwj8-xpvk")
casosPositius <- casosTotal %>% filter(resultatcoviddescripcio != 'Sospitós') #This is no longer needed.
casosSospitos <- read.socrata("https://analisi.transparenciacatalunya.cat/api/odata/v4/dmzh-fz47")
# This is for the old verion of the database. Updatged on 2021/01/04
#casosSospitos <- casosTotal %>% filter(resultatcoviddescripcio == 'PCR probable')

casosDiaris <- aggregate(casosPositius$numcasos, by=list(casosPositius$data), sum)
colnames(casosDiaris) <- c("data","nous_casos_confirmats")

testsDiaris <- aggregate(casosSospitos$pcr, by=list(casosSospitos$data), sum)
colnames(testsDiaris) <- c("data","nous_tests_fets")

  Hospitalitzats <- read.socrata("https://analisi.transparenciacatalunya.cat/api/odata/v4/c7sd-zy9j")
  
  HospitalitzatsAll <- aggregate(Hospitalitzats$ingressats_total, by=list(Hospitalitzats$data), sum)
  HospitalitzatsAll$Group.1 <- as.Date(HospitalitzatsAll$Group.1 , format = "%y/%m/%d")
  
  HospitalitzatsSub09 <- Hospitalitzats %>% filter(grup_edat == '0 a 9')
  HospitalitzatsSub09 <- aggregate(HospitalitzatsSub09$ingressats_total, by=list(HospitalitzatsSub09$data), sum)
  HospitalitzatsSub09$Group.1 <- as.Date(HospitalitzatsSub09$Group.1 , format = "%y/%m/%d")
  
  HospitalitzatsSub19 <- Hospitalitzats %>% filter(grup_edat == '10 a 19')
  HospitalitzatsSub19 <- aggregate(HospitalitzatsSub19$ingressats_total, by=list(HospitalitzatsSub19$data), sum)
  HospitalitzatsSub19$Group.1 <- as.Date(HospitalitzatsSub19$Group.1 , format = "%y/%m/%d")
  
  HospitalitzatsSub29 <- Hospitalitzats %>% filter(grup_edat == '20 a 29')
  HospitalitzatsSub29 <- aggregate(HospitalitzatsSub29$ingressats_total, by=list(HospitalitzatsSub29$data), sum)
  HospitalitzatsSub29$Group.1 <- as.Date(HospitalitzatsSub29$Group.1 , format = "%y/%m/%d")

  HospitalitzatsSub39 <- Hospitalitzats %>% filter(grup_edat == '30 a 39')
  HospitalitzatsSub39 <- aggregate(HospitalitzatsSub39$ingressats_total, by=list(HospitalitzatsSub39$data), sum)
  HospitalitzatsSub39$Group.1 <- as.Date(HospitalitzatsSub39$Group.1 , format = "%y/%m/%d")

  HospitalitzatsSub49 <- Hospitalitzats %>% filter(grup_edat == '40 a 49')
  HospitalitzatsSub49 <- aggregate(HospitalitzatsSub49$ingressats_total, by=list(HospitalitzatsSub49$data), sum)
  HospitalitzatsSub49$Group.1 <- as.Date(HospitalitzatsSub49$Group.1 , format = "%y/%m/%d")
  
  HospitalitzatsSub59 <- Hospitalitzats %>% filter(grup_edat == '50 a 59')
  HospitalitzatsSub59 <- aggregate(HospitalitzatsSub59$ingressats_total, by=list(HospitalitzatsSub59$data), sum)
  HospitalitzatsSub59$Group.1 <- as.Date(HospitalitzatsSub59$Group.1 , format = "%y/%m/%d")

  HospitalitzatsSub69 <- Hospitalitzats %>% filter(grup_edat == '60 a 69')
  HospitalitzatsSub69 <- aggregate(HospitalitzatsSub69$ingressats_total, by=list(HospitalitzatsSub69$data), sum)
  HospitalitzatsSub69$Group.1 <- as.Date(HospitalitzatsSub69$Group.1 , format = "%y/%m/%d")

  HospitalitzatsSub79 <- Hospitalitzats %>% filter(grup_edat == '70 a 79')
  HospitalitzatsSub79 <- aggregate(HospitalitzatsSub79$ingressats_total, by=list(HospitalitzatsSub79$data), sum)
  HospitalitzatsSub79$Group.1 <- as.Date(HospitalitzatsSub79$Group.1 , format = "%y/%m/%d")

  HospitalitzatsSub89 <- Hospitalitzats %>% filter(grup_edat == '80 o més')
  HospitalitzatsSub89 <- aggregate(HospitalitzatsSub89$ingressats_total, by=list(HospitalitzatsSub89$data), sum)
  HospitalitzatsSub89$Group.1 <- as.Date(HospitalitzatsSub89$Group.1 , format = "%y/%m/%d")
  
  
  UCIsAll <- aggregate(Hospitalitzats$ingressats_critic, by=list(Hospitalitzats$data), sum)
  UCIsAll$Group.1 <- as.Date(UCIsAll$Group.1 , format = "%y/%m/%d")
  
  UCIsSub09 <- Hospitalitzats %>% filter(grup_edat == '0 a 9')
  UCIsSub09 <- aggregate(UCIsSub09$ingressats_critic, by=list(UCIsSub09$data), sum)
  UCIsSub09$Group.1 <- as.Date(UCIsSub09$Group.1 , format = "%y/%m/%d")
  
  UCIsSub19 <- Hospitalitzats %>% filter(grup_edat == '10 a 19')
  UCIsSub19 <- aggregate(UCIsSub19$ingressats_critic, by=list(UCIsSub19$data), sum)
  UCIsSub19$Group.1 <- as.Date(UCIsSub19$Group.1 , format = "%y/%m/%d")
  
  UCIsSub29 <- Hospitalitzats %>% filter(grup_edat == '20 a 29')
  UCIsSub29 <- aggregate(UCIsSub29$ingressats_critic, by=list(UCIsSub29$data), sum)
  UCIsSub29$Group.1 <- as.Date(UCIsSub29$Group.1 , format = "%y/%m/%d")

  UCIsSub39 <- Hospitalitzats %>% filter(grup_edat == '30 a 39')
  UCIsSub39 <- aggregate(UCIsSub39$ingressats_critic, by=list(UCIsSub39$data), sum)
  UCIsSub39$Group.1 <- as.Date(UCIsSub39$Group.1 , format = "%y/%m/%d")

  UCIsSub49 <- Hospitalitzats %>% filter(grup_edat == '40 a 49')
  UCIsSub49 <- aggregate(UCIsSub49$ingressats_critic, by=list(UCIsSub49$data), sum)
  UCIsSub49$Group.1 <- as.Date(UCIsSub49$Group.1 , format = "%y/%m/%d")
  
  UCIsSub59 <- Hospitalitzats %>% filter(grup_edat == '50 a 59')
  UCIsSub59 <- aggregate(UCIsSub59$ingressats_critic, by=list(UCIsSub59$data), sum)
  UCIsSub59$Group.1 <- as.Date(UCIsSub59$Group.1 , format = "%y/%m/%d")

  UCIsSub69 <- Hospitalitzats %>% filter(grup_edat == '60 a 69')
  UCIsSub69 <- aggregate(UCIsSub69$ingressats_critic, by=list(UCIsSub69$data), sum)
  UCIsSub69$Group.1 <- as.Date(UCIsSub69$Group.1 , format = "%y/%m/%d")

  UCIsSub79 <- Hospitalitzats %>% filter(grup_edat == '70 a 79')
  UCIsSub79 <- aggregate(UCIsSub79$ingressats_critic, by=list(UCIsSub79$data), sum)
  UCIsSub79$Group.1 <- as.Date(UCIsSub79$Group.1 , format = "%y/%m/%d")

  UCIsSub89 <- Hospitalitzats %>% filter(grup_edat == '80 o més')
  UCIsSub89 <- aggregate(UCIsSub89$ingressats_critic, by=list(UCIsSub89$data), sum)
  UCIsSub89$Group.1 <- as.Date(UCIsSub89$Group.1 , format = "%y/%m/%d")
  
  #Morts
  ExitusAll <- aggregate(Hospitalitzats$exitus, by=list(Hospitalitzats$data), sum)
  ExitusAll$Group.1 <- as.Date(ExitusAll$Group.1 , format = "%y/%m/%d")
  
  ExitusSub09 <- Hospitalitzats %>% filter(grup_edat == '0 a 9')
  ExitusSub09 <- aggregate(ExitusSub09$exitus, by=list(ExitusSub09$data), sum)
  ExitusSub09$Group.1 <- as.Date(ExitusSub09$Group.1 , format = "%y/%m/%d")
  
  ExitusSub19 <- Hospitalitzats %>% filter(grup_edat == '10 a 19')
  ExitusSub19 <- aggregate(ExitusSub19$exitus, by=list(ExitusSub19$data), sum)
  ExitusSub19$Group.1 <- as.Date(ExitusSub19$Group.1 , format = "%y/%m/%d")
  
  ExitusSub29 <- Hospitalitzats %>% filter(grup_edat == '20 a 29')
  ExitusSub29 <- aggregate(ExitusSub29$exitus, by=list(ExitusSub29$data), sum)
  ExitusSub29$Group.1 <- as.Date(ExitusSub29$Group.1 , format = "%y/%m/%d")

  ExitusSub39 <- Hospitalitzats %>% filter(grup_edat == '30 a 39')
  ExitusSub39 <- aggregate(ExitusSub39$exitus, by=list(ExitusSub39$data), sum)
  ExitusSub39$Group.1 <- as.Date(ExitusSub39$Group.1 , format = "%y/%m/%d")

  ExitusSub49 <- Hospitalitzats %>% filter(grup_edat == '40 a 49')
  ExitusSub49 <- aggregate(ExitusSub49$exitus, by=list(ExitusSub49$data), sum)
  ExitusSub49$Group.1 <- as.Date(ExitusSub49$Group.1 , format = "%y/%m/%d")
  
  ExitusSub59 <- Hospitalitzats %>% filter(grup_edat == '50 a 59')
  ExitusSub59 <- aggregate(ExitusSub59$exitus, by=list(ExitusSub59$data), sum)
  ExitusSub59$Group.1 <- as.Date(ExitusSub59$Group.1 , format = "%y/%m/%d")

  ExitusSub69 <- Hospitalitzats %>% filter(grup_edat == '60 a 69')
  ExitusSub69 <- aggregate(ExitusSub69$exitus, by=list(ExitusSub69$data), sum)
  ExitusSub69$Group.1 <- as.Date(ExitusSub69$Group.1 , format = "%y/%m/%d")

  ExitusSub79 <- Hospitalitzats %>% filter(grup_edat == '70 a 79')
  ExitusSub79 <- aggregate(ExitusSub79$exitus, by=list(ExitusSub79$data), sum)
  ExitusSub79$Group.1 <- as.Date(ExitusSub79$Group.1 , format = "%y/%m/%d")

  ExitusSub89 <- Hospitalitzats %>% filter(grup_edat == '80 o més')
  ExitusSub89 <- aggregate(ExitusSub89$exitus, by=list(ExitusSub89$data), sum)
  ExitusSub89$Group.1 <- as.Date(ExitusSub89$Group.1 , format = "%y/%m/%d")
  
  # Vaccination process
  
  Vacunacions <- read.socrata("https://analisi.transparenciacatalunya.cat/api/odata/v4/cuwj-bh3b")
  VacunacionsDosi1 <- Vacunacions %>% filter(dosi == '1')
  VacunacionsDosi2 <- Vacunacions %>% filter(dosi == '2')

  # VacunacionsDosi1Nens <- VacunacionsDosi1 %>% filter(edat == 'Menors de 15')
  # VacunacionsDosi1Adults <- VacunacionsDosi1 %>% filter(edat == '15 a 64')  
  # VacunacionsDosi1Grans <- VacunacionsDosi1 %>% filter(edat == '65 a 74')  
  # VacunacionsDosi1Avis <- VacunacionsDosi1 %>% filter(edat == '75 o més') 
  
  VacunacionsDosi1All <- aggregate(VacunacionsDosi1$recompte, by=list(VacunacionsDosi1$data), sum)
  VacunacionsDosi1All$Group.1 <- as.Date(VacunacionsDosi1All$Group.1 , format = "%y/%m/%d")
  
  VacunacionsDosi2All <- aggregate(VacunacionsDosi2$recompte, by=list(VacunacionsDosi2$data), sum)
  VacunacionsDosi2All$Group.1 <- as.Date(VacunacionsDosi2All$Group.1 , format = "%y/%m/%d")
  
# ICRA
  # EDAR a analitzar
  
# CODI	NOM EDAR	Freq de mostreig
# DABR	ABRERA	Setmanal
# DAMP	AMPOSTA	Setmanal
# DBAL	BALAGUER	Setmanal
# DBAY	BANYOLES	Setmanal
# DBER	BERGA	Setmanal
# DBSS	BESÒS	Setmanal
# DFAL	FALSET	Setmanal
# DFIG	FIGUERES	Setmanal
# DGIR	GIRONA	Setmanal
# DGRA	GRANOLLERS	Setmanal
# DGVC	GAVÀ/VILADECANS	Setmanal
# DIGU	IGUALADA	Setmanal
# DLLE	LLEIDA	Setmanal
# DMAN	MANLLEU	Setmanal
# DMAS	MANRESA	Setmanal
# DMAT	MATARÓ	Setmanal
# DMIR	MONTCADA	Setmanal
# DMOF	MONTFERRER	Setmanal
# DMRT	MARTORELL	Setmanal
# DOLO	OLOT	Setmanal
# DPAM	PALAMÓS	Setmanal 
# DPDL	PRAT DE LLOBREGAT, EL	Setmanal
# DPUI	PUIGCERDÀ	Setmanal
# DRIP	RIPOLL	Setmanal
# DRUB	RUBÍ	Setmanal
# DRUS	REUS	Setmanal
# DSFL	SANT FELIU DE LLOBREGAT	Setmanal
# DSLL	SALLENT/ARTÉS	Setmanal
# DSOL	SOLSONA	Setmanal
# DSRS	SABADELL/RIU SEC	Setmanal
# DTAR	TARRAGONA	Setmanal
# DTOT	TORTOSA-ROQUETES	Setmanal
# DTRS	TERRASSA	Setmanal
# DVDP	VILAFRANCA DEL PENEDÈS	Setmanal
# DVEN	RIERA DE LA BISBAL	Setmanal
# DVIC	VIC	Setmanal
# DVLG	VILANOVA I LA GELTRÚ	Setmanal

# Servei per obtenir la informació de l'aigua
url <- "https://apicovid.icradev.cat/n1"
#En cas que el servei falli
file <- "ICRA_dataACT.csv"
# cabal*1000/depuradores

#ICRA_data <- readUrl(url,file)
ICRA_data <- read.csv2(file)

## ICRA_data$Data.mostreig <- as.Date(ICRA_data$Data.mostreig , format = "%Y-%m-%d")

# write.csv2(ICRA_data, file="ICRA_dataACT.csv")

#DIGITAL TWIN
# ##################################################################################

# infective <- read.csv2("../../models/SDL/Pandemiav1.9/experiment/6200/data/traces/totalInfective.csv")
# recovered <- read.csv2("../../models/SDL/Pandemiav1.9/experiment/6200/data/traces/totalRecovered.csv")
# deaths <- read.csv2("../../models/SDL/Pandemiav1.9/experiment/6200/data/traces/totalDeceased.csv")

# newInfectives <- read.csv2("../../models/SDL/Pandemiav1.9/experiment/catalunya/data/traces/newInfectiveDetectedDiary.csv")
# 
# # The SDL model starts on 29 of january, since the model works with deltat=0.1 we must agrupate every 10 points.
# # We lselect the values withouth decimal values, 1 of each 10.
# index = c(1:(length(newInfectives$time)/10))
# dt1 <- rep(as.Date("2020-01-29 CET"),length(index))
# datetimes<-dt1+index
# values<-newInfectives$values[newInfectives$time %in% index]
# newInfectives<-data.frame(datetimes,values)
# 
# newInfectives2.5 <- read.csv2("../../models/SDL/Pandemiav2.5/experiment/catalunya/data/traces/newInfectiveDetectedDiary.csv")
# 
# # El model sdlps comença el dia 29 de gener, seleccionem només els valors dels dts sense decimals, 1 de cada 10.
# index = c(1:(length(newInfectives2.5$time)/10))
# dt1 <- rep(as.Date("2020-01-29 CET"),length(index))
# datetimes<-dt1+index
# values<-newInfectives2.5$values[newInfectives2.5$time %in% index]
# newInfectives2.5<-data.frame(datetimes,values)

onlyOneModel = FALSE

#Cal afegir les dades del model a casosDiaris
# nous_casos_model <- read.csv("../new_cases.csv", header = FALSE)
# casosDiaris$model1.7<-nous_casos_model[31:(dim(casosDiaris)[1]+30),]
# 
casosDiaris$m_3<-ma(casosDiaris$nous_casos_confirmats,3)
casosDiaris$m_7<-ma(casosDiaris$nous_casos_confirmats,7)
casosDiaris$m_14<-ma(casosDiaris$nous_casos_confirmats,14)

#Guardar en csv els casos diaris
write.csv(casosDiaris,"./casosDiarisLAST.csv",row.names = FALSE)

```
Introduction {data-icon="fa-list"}
===============================================================

Row
-----------------------------------------------------------------------
### Detected new cases model 2.10 {data-padding=50}
From the current version of the model (2.10) the forecast tries to find the current number of real cases. Until version 2.9 the aim of the model was to show a pessimistic scenario with a maximum number of cases, this is the reason why the forecasts moves in the upper threshold of the detected cases curve. Therefore, 2.10 previsions for detected cases is below other previous previsions. An attempt to describe the drivers of the spread in Catalonia can be reviewed at http://pand.sdlps.com/Pandemic-drivers.html

```{r plotIntro, echo=FALSE}


```


Row
-----------------------------------------------------------------------
### Information 
This panel starts with the SDL-PAND project.

```{r intro, echo=FALSE}

htmltools::includeHTML("intro/intro.html")

```

All Catalunya {data-icon="fa-hashtag"}
===============================================================

Row Row {.tabset .tabset-fade}
-----------------------------------------------------------------------

### New cases {data-padding=50}
The simulation model allows to have a forecast of the evolution of the pandemic. It is corrected based on the actual data of the evolution of the pandemic. The current model is model 2.10. The R is calculated with the EpiEstim package of the statistical language "R".

```{r plotModel, echo=FALSE}


```


### R valueR
```{r R_calculus, echo=FALSE}
```

Row
-----------------------------------------------------------------------
### Effective growth
```{r day_cases, echo=FALSE}
```
C3: 3 days moving average; C7: 7 days moving average; C14: 14 days moving average. C7 and C14 are more stable than C3, picking up trend variations in full week. Especially C3 has bias, an increase (very unstable) may represent a quick warning of possible worsening.

### Incidence
```{r R_incidencia, echo=FALSE}
```
Incidence of the pandemic in the population, per 100,000 inhabitants.

### Situation reported in Catalonia

```{r situationPercent, echo=FALSE}

file = paste("../../models/SDL/",currentModel,"/regions-ALL/newInfectiveDiary.csv",sep="")
newInfectives2.9 <- read.csv2(file)

index = c(0:((length(newInfectives2.9$cell_time)-1)/10))
index = index+newInfectives2.9$cell_time[1]
dt1 <- rep(as.Date("2019-12-01 CET"),length(index))
datetimes<-dt1+index

values<-newInfectives2.9$cell_values[newInfectives2.9$cell_time %in% index]
newInfectives2.9<-data.frame(datetimes,values)

casosTotalsActuals<-sum(newInfectives2.9$values[datetimes<Sys.Date()])
casosTotalsFinal<-sum(newInfectives2.9$values[])

file = paste("../../models/SDL/",currentModel,"/regions-ALL/newExposedRecovered.csv",sep="")
newReinfections2.9 <- read.csv2(file)

casosReinfeccionsActuals<-sum(newReinfections2.9$values[datetimes<Sys.Date()])
casosReinfeccionsFinal<-sum(newReinfections2.9$values[])

casosRealsActuals<-casosTotalsActuals-casosReinfeccionsActuals
casosRealsFinal<-casosTotalsFinal-casosReinfeccionsFinal

casosDetectatsAcumulats <- sum(casosPositius$numcasos)

Positius=casosDetectatsAcumulats/PoblacioTotal
Undetected=(casosRealsActuals-casosDetectatsAcumulats)/PoblacioTotal
Total=1-Positius-Undetected

values <- list(Positius=Positius,Undetected=Undetected,Total=1-(Positius+Undetected))
personograph(values, n.icons=100, colors=list(Positius="red", Undetected="orange",Total="lightgreen"), draw.legend=TRUE, fig.cap = "", icon.style=3)

```

### Accumulated curve
```{r plotCumulativeCurve, echo=FALSE}
```

Row
-----------------------------------------------------------------------
### Total number of cases (detected, with reinfections).

```{r Current_casos, echo=FALSE}
valueBox(casosDetectatsAcumulats, icon = "fa-pencil")
```

### Actual number of cases (estimated, not considering reinfections)

```{r Current_casos_reals, echo=FALSE}

casosRealsActuals <- round(casosRealsActuals, digit=0)
valueBox(casosRealsActuals, icon = "fa-pencil")
```

### Actual number of cases at the end of the wave (estimated, not considering reinfections)

```{r Current_casos_reals_finalOnada, echo=FALSE}

casosRealsFinal <- round(casosRealsFinal, digit=0)
valueBox(casosRealsFinal, icon = "fa-pencil")
```

### New cases from the last day

```{r Current_data, echo=FALSE}
casosAhir=casosDiaris$nous_casos_confirmats[nrow(casosDiaris)]

valueBox(casosAhir, icon = "fa-pencil")
```

### Last day of system update

```{r last_updated, echo=FALSE}
```

Health system incidence {data-icon="fa-list"}
===============================================================


Row
-----------------------------------------------------------------------
### Hospitalizations
Hospitalizations.

```{r Hospitalitzacions, echo=FALSE}

fig <- plot_ly(type="bar", 
               x = HospitalitzatsAll$Group.1,
               y = HospitalitzatsAll$x,
               name = 'Hospitalizations',
               text = paste("New cases"))

fig <- fig %>% add_trace(y = HospitalitzatsSub09$x, x=HospitalitzatsSub09$Group.1, type='scatter', mode = 'lines', name='0 a 9')
fig <- fig %>% add_trace(y = HospitalitzatsSub19$x, x=HospitalitzatsSub19$Group.1, type='scatter', mode = 'lines', name='10 a 19')
fig <- fig %>% add_trace(y = HospitalitzatsSub29$x, x=HospitalitzatsSub29$Group.1, type='scatter', mode = 'lines', name='20 a 29')
fig <- fig %>% add_trace(y = HospitalitzatsSub39$x, x=HospitalitzatsSub39$Group.1, type='scatter', mode = 'lines', name='30 a 39')
fig <- fig %>% add_trace(y = HospitalitzatsSub49$x, x=HospitalitzatsSub49$Group.1, type='scatter', mode = 'lines', name='40 a 49')
fig <- fig %>% add_trace(y = HospitalitzatsSub59$x, x=HospitalitzatsSub59$Group.1, type='scatter', mode = 'lines', name='50 a 59')
fig <- fig %>% add_trace(y = HospitalitzatsSub69$x, x=HospitalitzatsSub69$Group.1, type='scatter', mode = 'lines', name='60 a 69')
fig <- fig %>% add_trace(y = HospitalitzatsSub79$x, x=HospitalitzatsSub79$Group.1, type='scatter', mode = 'lines', name='70 a 79')
fig <- fig %>% add_trace(y = HospitalitzatsSub89$x, x=HospitalitzatsSub89$Group.1, type='scatter', mode = 'lines', name='80 o més')
fig

```


Row
-----------------------------------------------------------------------

### UCIs
Critical hospitalizations.

```{r UCIs, echo=FALSE}

fig <- plot_ly(type="bar", 
               x = UCIsAll$Group.1,
               y = UCIsAll$x,
               name = 'UCIs',
               text = paste("New cases"))

fig <- fig %>% add_trace(y = UCIsSub09$x, x=UCIsSub09$Group.1, type='scatter', mode = 'lines', name='0 a 9')
fig <- fig %>% add_trace(y = UCIsSub19$x, x=UCIsSub19$Group.1, type='scatter', mode = 'lines', name='10 a 19')
fig <- fig %>% add_trace(y = UCIsSub29$x, x=UCIsSub29$Group.1, type='scatter', mode = 'lines', name='20 a 29')
fig <- fig %>% add_trace(y = UCIsSub39$x, x=UCIsSub39$Group.1, type='scatter', mode = 'lines', name='30 a 39')
fig <- fig %>% add_trace(y = UCIsSub49$x, x=UCIsSub49$Group.1, type='scatter', mode = 'lines', name='40 a 49')
fig <- fig %>% add_trace(y = UCIsSub59$x, x=UCIsSub59$Group.1, type='scatter', mode = 'lines', name='50 a 59')
fig <- fig %>% add_trace(y = UCIsSub69$x, x=UCIsSub69$Group.1, type='scatter', mode = 'lines', name='60 a 69')
fig <- fig %>% add_trace(y = UCIsSub79$x, x=UCIsSub79$Group.1, type='scatter', mode = 'lines', name='70 a 79')
fig <- fig %>% add_trace(y = UCIsSub89$x, x=UCIsSub89$Group.1, type='scatter', mode = 'lines', name='80 o més')
fig

```

Row
-----------------------------------------------------------------------
### Exitus
Daily deaths.

```{r Exitus, echo=FALSE}

fig <- plot_ly(type="bar",
               x = ExitusAll$Group.1,
               y = ExitusAll$x,
               name = 'Exitus',
               text = paste("New cases"))

fig <- fig %>% add_trace(y = ExitusSub09$x, x=ExitusSub09$Group.1, type='scatter', mode = 'lines', name='0 a 9')
fig <- fig %>% add_trace(y = ExitusSub19$x, x=ExitusSub19$Group.1, type='scatter', mode = 'lines', name='10 a 19')
fig <- fig %>% add_trace(y = ExitusSub29$x, x=ExitusSub29$Group.1, type='scatter', mode = 'lines', name='20 a 29')
fig <- fig %>% add_trace(y = ExitusSub39$x, x=ExitusSub39$Group.1, type='scatter', mode = 'lines', name='30 a 39')
fig <- fig %>% add_trace(y = ExitusSub49$x, x=ExitusSub49$Group.1, type='scatter', mode = 'lines', name='40 a 49')
fig <- fig %>% add_trace(y = ExitusSub59$x, x=ExitusSub59$Group.1, type='scatter', mode = 'lines', name='50 a 59')
fig <- fig %>% add_trace(y = ExitusSub69$x, x=ExitusSub69$Group.1, type='scatter', mode = 'lines', name='60 a 69')
fig <- fig %>% add_trace(y = ExitusSub79$x, x=ExitusSub79$Group.1, type='scatter', mode = 'lines', name='70 a 79')
fig <- fig %>% add_trace(y = ExitusSub89$x, x=ExitusSub89$Group.1, type='scatter', mode = 'lines', name='80 o més')
fig

```

Row
-----------------------------------------------------------------------
### Vaccinations First dose
Daily vaccinations (first dose, cumulative)

```{r vacunacions1, echo=FALSE}

fig <- plot_ly(type="bar", 
               x = VacunacionsDosi1All$Group.1,
               y = cumsum(VacunacionsDosi1All$x),
               name = 'First dose',
               text = paste("First dose (cases)"))

# fig <- fig %>% add_trace(y = cumsum(VacunacionsDosi1Nens$x), x=VacunacionsDosi1Nens$Group.1, type='scatter', mode = 'lines', name='0-15')
# fig <- fig %>% add_trace(y = cumsum(VacunacionsDosi1Adults$x), x=VacunacionsDosi1Adults$Group.1, type='scatter', mode = 'lines', name='15-64')
# fig <- fig %>% add_trace(y = cumsum(VacunacionsDosi1Grans$x), x=VacunacionsDosi1Grans$Group.1, type='scatter', mode = 'lines', name='65-74')
# fig <- fig %>% add_trace(y = cumsum(VacunacionsDosi1Avis$x), x=VacunacionsDosi1Avis$Group.1, type='scatter', mode = 'lines', name='75+')
fig

```

### Vaccinations Second dose
Daily vaccinations (second dose, cumulative)

```{r vacunacions2, echo=FALSE}

fig <- plot_ly(type="bar", 
               x = VacunacionsDosi2All$Group.1,
               y = cumsum(VacunacionsDosi2All$x),
               name = 'Second dose',
               text = paste("Second dose (cases)"))

# fig <- fig %>% add_trace(y = cumsum(VacunacionsDosi2Nens$x), x=VacunacionsDosi2Nens$Group.1, type='scatter', mode = 'lines', name='0-15')
# fig <- fig %>% add_trace(y = cumsum(VacunacionsDosi2Adults$x), x=VacunacionsDosi2Adults$Group.1, type='scatter', mode = 'lines', name='15-64')
# fig <- fig %>% add_trace(y = cumsum(VacunacionsDosi2Grans$x), x=VacunacionsDosi2Grans$Group.1, type='scatter', mode = 'lines', name='65-74')
# fig <- fig %>% add_trace(y = cumsum(VacunacionsDosi2Avis$x), x=VacunacionsDosi2Avis$Group.1, type='scatter', mode = 'lines', name='75+')
fig

```

Row
-----------------------------------------------------------------------
### Vaccinations% First Dose

```{r percetn_primeraDosi, echo=FALSE}

percentDosis <- round(sum(VacunacionsDosi1All$x)*100/PoblacioTotal, digits = 2)
valueBox(percentDosis, icon = "fa-pencil", color = ifelse(percentDosis < 70, "warning", "primary"))
```


### Vaccinations% Second Dose

```{r percetn_segonaDosi, echo=FALSE}
percentDosis <- round(sum(VacunacionsDosi2All$x)*100/PoblacioTotal,digits=2)
valueBox(percentDosis, icon = "fa-pencil", color = ifelse(percentDosis < 70, "warning", "primary"))
```

Health regions {data-icon="fa-list"}
===============================================================
### Catalonia Health Regions
The aim of modeling by health regions is not the forecast but the validation of the global forecast.

```{r map, echo=FALSE}

#htmltools::includeHTML("http://empty.polyhedra.tech/sdl-pandv1.9/map/map.html")
htmltools::includeHTML("Map/map.html")

```

EDAR {data-icon="fa-list"}
===============================================================
### Catalonia EDAR
The aim of modeling by EDAR is to perform a cross validation of the model previsions.

Row
-----------------------------------------------------------------------
###  Catalonia EDAR
Edar Besós - DBSS

```{r mapEDAR, echo=FALSE}

  # listEdars <- c("DBSS","DGIR","DLLE","DPDL")

  edar<-"DBSS"
  file = paste("../../models/SDL/",edarModel,"/regions-Edars/",edar,"_newInfectiveDiary.csv",sep="")
  
  newInfectives <- read.csv2(file)
  
  index = c(0:((length(newInfectives$cell_time)-1)/10))
  index = index+newInfectives$cell_time[1]
  dt1 <- rep(as.Date("2019-12-01 CET"),length(index))
  datetimes<-dt1+index
  
  values<-newInfectives$cell_values[newInfectives$cell_time %in% index]
  times<-newInfectives$cell_time[newInfectives$cell_time %in% index]
  dt1 <- rep(as.Date("2019-12-01 CET"),length(times))
  datetimes<-dt1+times
  newInfectives<-data.frame(datetimes,values)
  
  newInfectives<-newInfectives[newInfectives$datetimes>"2020-03-06",]
  
  ICRA_data_edar <- ICRA_data[ which(ICRA_data$Codi.EDAR==edar), ]
  ICRA_data_edar$LOG_N1<-log(ICRA_data_edar$N1..CG.L.)
  ICRA_data_edar$LOG_casos<-log(ICRA_data_edar$Positius.diagnosticats.municipis.servits..dia.mostreig)
  
  ICRA_data_edar$LOG_casos[which(!is.finite(ICRA_data_edar$LOG_casos))] <- 0
  
  ICRA_data_edar$LOG_casos[!is.finite(ICRA_data_edar$LOG_casos)] <- 0
  
  
  newInfectives$values<-log(newInfectives$values)
  
  newInfectives$values[which(!is.finite(newInfectives$values))] <- 0
  
  newInfectives$values[!is.finite(newInfectives$values)] <- 0
  
  fig <- plot_ly(type="bar",
                 x = ICRA_data_edar$Data.mostreig,
                 y = ICRA_data_edar$LOG_casos,
                 name = 'Casos detectats',
                 text = paste(""))
  
  fig <- fig %>% add_trace(y = ICRA_data_edar$LOG_N1, x=ICRA_data_edar$Data.mostreig, type='scatter', mode = 'lines', name='N1')
  fig <- fig %>% add_trace(y = newInfectives$values, x=newInfectives$datetimes, type='scatter', mode = 'lines', name='Casos SDL')
  fig

  
Grangers=NULL

Grangers <- data.frame(
  Lag=c("Lag 1", "Lag 2", "Lag 3", "Lag 4", "Lag 5", "Lag 6", "Lag 7", "Lag 8", "Lag 9", "Lag 10"),
  DBSS=c(0,0,0,0,0,0,0,0,0,0),
  DGIR=c(0,0,0,0,0,0,0,0,0,0),
  DLLE=c(0,0,0,0,0,0,0,0,0,0),
  DPDL=c(0,0,0,0,0,0,0,0,0,0)
  )

nLags=10;

i=1;
dependent=ICRA_data_edar$LOG_N1
independent=ICRA_data_edar$LOG_casos
# independent=newInfectives$values

while (i<=nLags)
{
  GRtest<-grangertest(dependent~independent, order=i)
  Grangers$DBSS[i]<-GRtest$`Pr(>F)`[2]
  i=i+1
}
```

Row
-----------------------------------------------------------------------
###  Catalonia EDAR
Edar Girona - DGIR

```{r mapEDARDGIR, echo=FALSE}

  # listEdars <- c("DBSS","DGIR","DLLE","DPDL")

  edar<-"DGIR"
  file = paste("../../models/SDL/",edarModel,"/regions-Edars/",edar,"_newInfectiveDiary.csv",sep="")
  
  newInfectives <- read.csv2(file)
  
  index = c(0:((length(newInfectives$cell_time)-1)/10))
  index = index+newInfectives$cell_time[1]
  dt1 <- rep(as.Date("2019-12-01 CET"),length(index))
  datetimes<-dt1+index
  
  values<-newInfectives$cell_values[newInfectives$cell_time %in% index]
  times<-newInfectives$cell_time[newInfectives$cell_time %in% index]
  dt1 <- rep(as.Date("2019-12-01 CET"),length(times))
  datetimes<-dt1+times
  newInfectives<-data.frame(datetimes,values)
  
  newInfectives<-newInfectives[newInfectives$datetimes>"2020-03-06",]
  
  ICRA_data_edar <- ICRA_data[ which(ICRA_data$Codi.EDAR==edar), ]
  ICRA_data_edar$LOG_N1<-log(ICRA_data_edar$N1..CG.L.)
  ICRA_data_edar$LOG_casos<-log(ICRA_data_edar$Positius.diagnosticats.municipis.servits..dia.mostreig)
  
  ICRA_data_edar$LOG_casos[which(!is.finite(ICRA_data_edar$LOG_casos))] <- 0
  
  ICRA_data_edar$LOG_casos[!is.finite(ICRA_data_edar$LOG_casos)] <- 0
  
  
  newInfectives$values<-log(newInfectives$values)
  
  newInfectives$values[which(!is.finite(newInfectives$values))] <- 0
  
  newInfectives$values[!is.finite(newInfectives$values)] <- 0
  
  fig <- plot_ly(type="bar",
                 x = ICRA_data_edar$Data.mostreig,
                 y = ICRA_data_edar$LOG_casos,
                 name = 'Casos detectats',
                 text = paste(""))
  
  fig <- fig %>% add_trace(y = ICRA_data_edar$LOG_N1, x=ICRA_data_edar$Data.mostreig, type='scatter', mode = 'lines', name='N1')
  fig <- fig %>% add_trace(y = newInfectives$values, x=newInfectives$datetimes, type='scatter', mode = 'lines', name='Casos SDL')
  fig

i=1;
dependent=ICRA_data_edar$LOG_N1
independent=ICRA_data_edar$LOG_casos

while (i<=nLags)
{
  GRtest<-grangertest(dependent~independent, order=i)
  Grangers$DGIR[i]<-GRtest$`Pr(>F)`[2]
  i=i+1
}

```

Row
-----------------------------------------------------------------------
###  Catalonia EDAR
Edar Lleida - DLLE

```{r mapEDARDLLE, echo=FALSE}

  # listEdars <- c("DBSS","DGIR","DLLE","DPDL")

  edar<-"DLLE"
  file = paste("../../models/SDL/",edarModel,"/regions-Edars/",edar,"_newInfectiveDiary.csv",sep="")
  
  newInfectives <- read.csv2(file)
  
  index = c(0:((length(newInfectives$cell_time)-1)/10))
  index = index+newInfectives$cell_time[1]
  dt1 <- rep(as.Date("2019-12-01 CET"),length(index))
  datetimes<-dt1+index
  
  values<-newInfectives$cell_values[newInfectives$cell_time %in% index]
  times<-newInfectives$cell_time[newInfectives$cell_time %in% index]
  dt1 <- rep(as.Date("2019-12-01 CET"),length(times))
  datetimes<-dt1+times
  newInfectives<-data.frame(datetimes,values)
  
  newInfectives<-newInfectives[newInfectives$datetimes>"2020-03-06",]
  
  ICRA_data_edar <- ICRA_data[ which(ICRA_data$Codi.EDAR==edar), ]
  ICRA_data_edar$LOG_N1<-log(ICRA_data_edar$N1..CG.L.)
  ICRA_data_edar$LOG_casos<-log(ICRA_data_edar$Positius.diagnosticats.municipis.servits..dia.mostreig)
  
  ICRA_data_edar$LOG_casos[which(!is.finite(ICRA_data_edar$LOG_casos))] <- 0
  
  ICRA_data_edar$LOG_casos[!is.finite(ICRA_data_edar$LOG_casos)] <- 0
  
  
  newInfectives$values<-log(newInfectives$values)
  
  newInfectives$values[which(!is.finite(newInfectives$values))] <- 0
  
  newInfectives$values[!is.finite(newInfectives$values)] <- 0
  
  fig <- plot_ly(type="bar",
                 x = ICRA_data_edar$Data.mostreig,
                 y = ICRA_data_edar$LOG_casos,
                 name = 'Casos detectats',
                 text = paste(""))
  
  fig <- fig %>% add_trace(y = ICRA_data_edar$LOG_N1, x=ICRA_data_edar$Data.mostreig, type='scatter', mode = 'lines', name='N1')
  fig <- fig %>% add_trace(y = newInfectives$values, x=newInfectives$datetimes, type='scatter', mode = 'lines', name='Casos SDL')
  fig

i=1;
dependent=ICRA_data_edar$LOG_N1
independent=ICRA_data_edar$LOG_casos

while (i<=nLags)
{
  GRtest<-grangertest(dependent~independent, order=i)
  Grangers$DLLE[i]<-GRtest$`Pr(>F)`[2]
  i=i+1
}

```

Row
-----------------------------------------------------------------------
###  Catalonia EDAR
Edar Llobregat - DPDL

```{r mapEDARDPDL, echo=FALSE}

  # listEdars <- c("DBSS","DGIR","DLLE","DPDL")

  edar<-"DPDL"
  file = paste("../../models/SDL/",edarModel,"/regions-Edars/",edar,"_newInfectiveDiary.csv",sep="")
  
  newInfectives <- read.csv2(file)
  
  index = c(0:((length(newInfectives$cell_time)-1)/10))
  index = index+newInfectives$cell_time[1]
  dt1 <- rep(as.Date("2019-12-01 CET"),length(index))
  datetimes<-dt1+index
  
  values<-newInfectives$cell_values[newInfectives$cell_time %in% index]
  times<-newInfectives$cell_time[newInfectives$cell_time %in% index]
  dt1 <- rep(as.Date("2019-12-01 CET"),length(times))
  datetimes<-dt1+times
  newInfectives<-data.frame(datetimes,values)
  
  newInfectives<-newInfectives[newInfectives$datetimes>"2020-03-06",]
  
  ICRA_data_edar <- ICRA_data[ which(ICRA_data$Codi.EDAR==edar), ]
  ICRA_data_edar$LOG_N1<-log(ICRA_data_edar$N1..CG.L.)
  ICRA_data_edar$LOG_casos<-log(ICRA_data_edar$Positius.diagnosticats.municipis.servits..dia.mostreig)
  
  ICRA_data_edar$LOG_casos[which(!is.finite(ICRA_data_edar$LOG_casos))] <- 0
  
  ICRA_data_edar$LOG_casos[!is.finite(ICRA_data_edar$LOG_casos)] <- 0
  
  
  newInfectives$values<-log(newInfectives$values)
  
  newInfectives$values[which(!is.finite(newInfectives$values))] <- 0
  
  newInfectives$values[!is.finite(newInfectives$values)] <- 0
  
  fig <- plot_ly(type="bar",
                 x = ICRA_data_edar$Data.mostreig,
                 y = ICRA_data_edar$LOG_casos,
                 name = 'Casos detectats',
                 text = paste(""))
  
  fig <- fig %>% add_trace(y = ICRA_data_edar$LOG_N1, x=ICRA_data_edar$Data.mostreig, type='scatter', mode = 'lines', name='N1')
  fig <- fig %>% add_trace(y = newInfectives$values, x=newInfectives$datetimes, type='scatter', mode = 'lines', name='Casos SDL')
  fig

i=1;
dependent=ICRA_data_edar$LOG_N1
independent=ICRA_data_edar$LOG_casos

while (i<=nLags)
{
  GRtest<-grangertest(dependent~independent, order=i)
  Grangers$DPDL[i]<-GRtest$`Pr(>F)`[2]
  i=i+1
}

knitr::kable(Grangers, digits=3)

```


Row
-----------------------------------------------------------------------
###  Catalonia EDAR
Edar Tarragona - DTAR

```{r mapEDARDTAR, echo=FALSE}

  # listEdars <- c("DBSS","DGIR","DLLE","DPDL")

  edar<-"DTAR"
  file = paste("../../models/SDL/",edarModel,"/regions-Edars/",edar,"_newInfectiveDiary.csv",sep="")
  
  newInfectives <- read.csv2(file)
  
  index = c(0:((length(newInfectives$cell_time)-1)/10))
  index = index+newInfectives$cell_time[1]
  dt1 <- rep(as.Date("2019-12-01 CET"),length(index))
  datetimes<-dt1+index
  
  values<-newInfectives$cell_values[newInfectives$cell_time %in% index]
  times<-newInfectives$cell_time[newInfectives$cell_time %in% index]
  dt1 <- rep(as.Date("2019-12-01 CET"),length(times))
  datetimes<-dt1+times
  newInfectives<-data.frame(datetimes,values)
  
  newInfectives<-newInfectives[newInfectives$datetimes>"2020-03-06",]
  
  ICRA_data_edar <- ICRA_data[ which(ICRA_data$Codi.EDAR==edar), ]
  ICRA_data_edar$LOG_N1<-log(ICRA_data_edar$N1..CG.L.)
  ICRA_data_edar$LOG_casos<-log(ICRA_data_edar$Positius.diagnosticats.municipis.servits..dia.mostreig)
  
  ICRA_data_edar$LOG_casos[which(!is.finite(ICRA_data_edar$LOG_casos))] <- 0
  
  ICRA_data_edar$LOG_casos[!is.finite(ICRA_data_edar$LOG_casos)] <- 0
  
  
  newInfectives$values<-log(newInfectives$values)
  
  newInfectives$values[which(!is.finite(newInfectives$values))] <- 0
  
  newInfectives$values[!is.finite(newInfectives$values)] <- 0
  
  fig <- plot_ly(type="bar",
                 x = ICRA_data_edar$Data.mostreig,
                 y = ICRA_data_edar$LOG_casos,
                 name = 'Casos detectats',
                 text = paste(""))
  
  fig <- fig %>% add_trace(y = ICRA_data_edar$LOG_N1, x=ICRA_data_edar$Data.mostreig, type='scatter', mode = 'lines', name='N1')
  fig <- fig %>% add_trace(y = newInfectives$values, x=newInfectives$datetimes, type='scatter', mode = 'lines', name='Casos SDL')
  fig

```

Row
-----------------------------------------------------------------------
###  Catalonia EDAR
Edar Manresa - DMAS

```{r mapEDARDMAS, echo=FALSE}

  # listEdars <- c("DBSS","DGIR","DLLE","DPDL")

  edar<-"DMAS"
  file = paste("../../models/SDL/",edarModel,"/regions-Edars/",edar,"_newInfectiveDiary.csv",sep="")
  
  newInfectives <- read.csv2(file)
  
  index = c(0:((length(newInfectives$cell_time)-1)/10))
  index = index+newInfectives$cell_time[1]
  dt1 <- rep(as.Date("2019-12-01 CET"),length(index))
  datetimes<-dt1+index
  
  values<-newInfectives$cell_values[newInfectives$cell_time %in% index]
  times<-newInfectives$cell_time[newInfectives$cell_time %in% index]
  dt1 <- rep(as.Date("2019-12-01 CET"),length(times))
  datetimes<-dt1+times
  newInfectives<-data.frame(datetimes,values)
  
  newInfectives<-newInfectives[newInfectives$datetimes>"2020-03-06",]
  
  ICRA_data_edar <- ICRA_data[ which(ICRA_data$Codi.EDAR==edar), ]
  ICRA_data_edar$LOG_N1<-log(ICRA_data_edar$N1..CG.L.)
  ICRA_data_edar$LOG_casos<-log(ICRA_data_edar$Positius.diagnosticats.municipis.servits..dia.mostreig)
  
  ICRA_data_edar$LOG_casos[which(!is.finite(ICRA_data_edar$LOG_casos))] <- 0
  
  ICRA_data_edar$LOG_casos[!is.finite(ICRA_data_edar$LOG_casos)] <- 0
  
  
  newInfectives$values<-log(newInfectives$values)
  
  newInfectives$values[which(!is.finite(newInfectives$values))] <- 0
  
  newInfectives$values[!is.finite(newInfectives$values)] <- 0
  
  fig <- plot_ly(type="bar",
                 x = ICRA_data_edar$Data.mostreig,
                 y = ICRA_data_edar$LOG_casos,
                 name = 'Casos detectats',
                 text = paste(""))
  
  fig <- fig %>% add_trace(y = ICRA_data_edar$LOG_N1, x=ICRA_data_edar$Data.mostreig, type='scatter', mode = 'lines', name='N1')
  fig <- fig %>% add_trace(y = newInfectives$values, x=newInfectives$datetimes, type='scatter', mode = 'lines', name='Casos SDL')
  fig

```

Model history {data-icon="fa-list"}
===============================================================
### Previous models
Here we have the models that we have been developing and that have been invalidated by the non-pharmaceutical actions applied to reduce the spread of the virus.
```{r plothistoria, echo=FALSE}


```
